### 2019-03-12 manuscript.rmd
polished some tables, changed Apolemia cnidoband sizes from 0 to NA

```{r phylosignals}
phylosignals = as.data.frame(matrix(ncol=3, nrow=ncol(sharedmean_logs[,-1])))
#phylosignals = as.data.frame(matrix(ncol=3, nrow=ncol(sharedmeans[,-1])))
names(phylosignals) = c("K", "P", "Ntaxa")
for(i in 2:ncol(sharedmean_logs)){
  CH_I=as.numeric(sharedmean_logs[,i])
  #CH_I=as.numeric(sharedmeans[,i])
  names(CH_I) = sharedmean_logs$Species
  #names(CH_I) = sharedmeans$Species
  SE_I = as.numeric(castSE[,i]) %>% log()
  SE_I[which(SE_I==-Inf)] = 0
  names(SE_I) = castSE$Species
  CH_I= CH_I[!is.na(CH_I)]
  SE_I= SE_I[!is.na(SE_I)]
  SE_I = SE_I[which(names(SE_I)%in%names(CH_I))]
  CH_I = CH_I[which(names(CH_I)%in%names(SE_I))]
  treeI = drop.tip(ultram,which(!(ultram$tip.label %in% names(CH_I))))
  class(treeI) = "phylo"
  #print(names(sharedmeans)[i]);print(phylosig(treeI, CH_I, se = SE_I, test=T) %>% .[c("K","P")])
  rownames(phylosignals)[i-1] <- names(sharedmean_logs)[i]
  PSIG <- phylosig(treeI, CH_I, se = SE_I, test=T)
  phylosignals[i-1,1] <- PSIG$K
  phylosignals[i-1,2] <- PSIG$P
  phylosignals[i-1,3] <- length(CH_I)
  phylosignals$K = round(phylosignals$K,3)
}
write.csv(phylosignals, "PhylosignalsWSE_log.csv")
```

@@

```{r prey-character-assoc}
#Phylogenetic ANOVAS with prey type presence
pANOVAs_diet = as.data.frame(matrix(ncol=ncol(dprunedmatrix_logs[,-1]), nrow=ncol(diet)))
rownames(pANOVAs_diet) = names(diet)
colnames(pANOVAs_diet) = names(dprunedmatrix_logs[,-1])
for(prey in 1:ncol(diet)){
  CH_J=diet[,prey]
  names(CH_J) = rownames(diet)
  for(char in 1:ncol(dprunedmatrix_logs[,-1])){
    CH_I = dprunedmatrix_logs[,char+1]
    names(CH_I) = dprunedmatrix_logs$Species
    CH_I = CH_I[!is.na(CH_I)]
    CH_J = CH_J[which(names(CH_J)%in%names(CH_I))]
    treeIJ = drop.tip(dprunedTree, which(!(dprunedTree$tip.label %in% names(CH_I))))
    if(length(unique(CH_I))>1 & length(unique(CH_J))>1){
    #phylANOVA(treeIJ,x=CH_J,y=CH_I) %>% .$Pf -> pANOVAs_diet[prey,char]
       #phylANOVA(treeIJ,x=CH_J,y=CH_I) %>% .$Pf -> pANOVAs_diet[prey,char]
    gls(CH_I ~ CH_J, correlation =  corBrownian(phy = treeIJ), data = as.data.frame(cbind(CH_I,CH_J)), method = "ML") %>% summary() %>% .$tTable %>% as.data.frame() %>% .$p %>% .[2] -> pANOVAs_diet[prey,char]
  }
  }}
pANOVAs_diet = pANOVAs_diet[,-1]
pANOVAs_diet[pANOVAs_diet>0.05] <- NA
write.csv(pANOVAs_diet, "pANOVAS_Diet.csv")

@@

#LOGISTIC REGRESSION
copepod = diet$`Copepod diet`
names(copepod) = rownames(diet)
heteroneme_elongation = dprunedmatrix_logs$heteroneme_elongation
names(heteroneme_elongation) = dprunedmatrix_logs$Species
copepod = copepod[match(dprunedTree$tip.label, names(copepod))]
heteroneme_elongation = heteroneme_elongation[match(dprunedTree$tip.label, names(heteroneme_elongation))]
dat = data.frame(heteroneme_elongation, copepod)
dat = dat[which(!is.nan(dat$heteroneme_elongation)),]
null = dat
null$heteroneme_elongation = rep(1, nrow(dat))
xtree = drop.tip(dprunedTree, which(!(dprunedTree$tip.label %in% rownames(dat))))
logit = phyloglm(copepod~heteroneme_elongation,phy=xtree,data=dat,boot=100)
logit = phyloglm(copepod~,phy=xtree,data=null,boot=100)
summary(logit)
coef(logit)
vcov(logit)
nlogit = glm(copepod~heteroneme_elongation,data=dat, family="binomial")

logits = data.frame(matrix(ncol = 9, nrow = 0))
names(logits) = c("Prey type", "Character", "Ntaxa", "phyloglmAIC", "phyloglmP","phyloglm_b","glmAIC", "glmP", "glm_b")
logit_diet = diet[,-7]
logits[1,] = rep(1,9)
for(prey in 1:ncol(logit_diet)){
  for(char in 2:ncol(dprunedmatrix_logs)){
    CH_J=logit_diet[,prey]
    names(CH_J) = rownames(logit_diet)
    CH_I = dprunedmatrix_logs[,char]
    names(CH_I) = dprunedmatrix_logs$Species
    CH_I = CH_I[!is.na(CH_I)]
    CH_J = CH_J[which(names(CH_J)%in%names(CH_I))]
    treeIJ = drop.tip(dprunedTree, which(!(dprunedTree$tip.label %in% names(CH_J))))
    CH_I = CH_I[match(treeIJ$tip.label, names(CH_I))]
    CH_J = CH_J[match(treeIJ$tip.label, names(CH_J))]
    datIJ = data.frame(preytype = CH_J, character = CH_I)
      if(length(unique(CH_I))>1 & length(unique(CH_J))>1){
      logit = glm(preytype~character,data=datIJ, family="binomial")
      print(logit)
      phylogit = phyloglm(preytype~character,phy=treeIJ,data=datIJ,boot=10, btol=30)
      print(phylogit)
      rowIJ = c(names(logit_diet)[prey], names(dprunedmatrix_logs)[char], phylogit$n, phylogit$aic, coef(summary(phylogit))[2,6], coef(summary(phylogit))[2,1], logit$aic, coef(summary(logit))[2,4], coef(summary(logit))[2,1])
      } else{
      rowIJ = c(names(logit_diet)[prey], names(dprunedmatrix_logs)[char], NA, NA, NA, NA, NA, NA, NA)
      }
    print(rowIJ)
    logits = rbind(logits, rowIJ)
  }
}
logits = logits[-1,]
logits[,4:9] = sapply(logits[,4:9], as.numeric)
logits[,4:9] = sapply(logits[,4:9], function(x){round(x,3)})
write.csv(logits, "diet_morph_logits.csv", row.names = F)

>>>>

```{r phylosignals}
phylosignals = as.data.frame(matrix(ncol=3, nrow=ncol(sharedmean_logs[,-1])))
#phylosignals = as.data.frame(matrix(ncol=3, nrow=ncol(sharedmeans[,-1])))
names(phylosignals) = c("K", "P", "Ntaxa")
for(i in 2:ncol(sharedmean_logs)){
  CH_I=as.numeric(sharedmean_logs[,i])
  #CH_I=as.numeric(sharedmeans[,i])
  names(CH_I) = sharedmean_logs$Species
  #names(CH_I) = sharedmeans$Species
  SE_I = as.numeric(castSE[,i]) %>% log()
  SE_I[which(SE_I==-Inf)] = 0
  names(SE_I) = castSE$Species
  CH_I= CH_I[!is.na(CH_I)]
  SE_I= SE_I[!is.na(SE_I)]
  SE_I = SE_I[which(names(SE_I)%in%names(CH_I))]
  CH_I = CH_I[which(names(CH_I)%in%names(SE_I))]
  treeI = drop.tip(ultram,which(!(ultram$tip.label %in% names(CH_I))))
  class(treeI) = "phylo"
  #print(names(sharedmeans)[i]);print(phylosig(treeI, CH_I, se = SE_I, test=T) %>% .[c("K","P")])
  rownames(phylosignals)[i-1] <- names(sharedmean_logs)[i]
  PSIG <- phylosig(treeI, CH_I, se = SE_I, test=T)
  phylosignals[i-1,1] <- PSIG$K
  phylosignals[i-1,2] <- PSIG$P
  phylosignals[i-1,3] <- length(CH_I)
  phylosignals$K = round(phylosignals$K,3)
}
#write.csv(phylosignals, "PhylosignalsWSE_log.csv")
```

@@

```{r prey-character-assoc}
#Phylogenetic ANOVAS with prey type presence
pANOVAs_diet = as.data.frame(matrix(ncol=ncol(dprunedmatrix_logs[,-1]), nrow=ncol(diet)))
rownames(pANOVAs_diet) = names(diet)
colnames(pANOVAs_diet) = names(dprunedmatrix_logs[,-1])
for(prey in 1:ncol(diet)){
  CH_J=diet[,prey]
  names(CH_J) = rownames(diet)
  for(char in 1:ncol(dprunedmatrix_logs[,-1])){
    CH_I = dprunedmatrix_logs[,char+1]
    names(CH_I) = dprunedmatrix_logs$Species
    CH_I = CH_I[!is.na(CH_I)]
    CH_J = CH_J[which(names(CH_J)%in%names(CH_I))]
    treeIJ = drop.tip(dprunedTree, which(!(dprunedTree$tip.label %in% names(CH_I))))
    if(length(unique(CH_I))>1 & length(unique(CH_J))>1){
    #phylANOVA(treeIJ,x=CH_J,y=CH_I) %>% .$Pf -> pANOVAs_diet[prey,char]
       #phylANOVA(treeIJ,x=CH_J,y=CH_I) %>% .$Pf -> pANOVAs_diet[prey,char]
    gls(CH_I ~ CH_J, correlation =  corBrownian(phy = treeIJ), data = as.data.frame(cbind(CH_I,CH_J)), method = "ML") %>% summary() %>% .$tTable %>% as.data.frame() %>% .$p %>% .[2] -> pANOVAs_diet[prey,char]
  }
  }}
pANOVAs_diet = pANOVAs_diet[,-1]
pANOVAs_diet[pANOVAs_diet>0.05] <- NA
#write.csv(pANOVAs_diet, "pANOVAS_Diet.csv")

@@

#LOGISTIC REGRESSION
logits = data.frame(matrix(ncol = 9, nrow = 0))
names(logits) = c("Prey type", "Character", "Ntaxa", "phyloglmAIC", "phyloglmP","phyloglm_b","glmAIC", "glmP", "glm_b")
logit_diet = diet[,-7]
logits[1,] = rep(1,9)
for(prey in 1:ncol(logit_diet)){
  for(char in 2:ncol(dprunedmatrix_logs)){
    CH_J=logit_diet[,prey]
    names(CH_J) = rownames(logit_diet)
    CH_I = dprunedmatrix_logs[,char]
    names(CH_I) = dprunedmatrix_logs$Species
    CH_I = CH_I[!is.na(CH_I)]
    CH_J = CH_J[which(names(CH_J)%in%names(CH_I))]
    treeIJ = drop.tip(dprunedTree, which(!(dprunedTree$tip.label %in% names(CH_J))))
    CH_I = CH_I[match(treeIJ$tip.label, names(CH_I))]
    CH_J = CH_J[match(treeIJ$tip.label, names(CH_J))]
    datIJ = data.frame(preytype = CH_J, character = CH_I)
      if(length(unique(CH_I))>1 & length(unique(CH_J))>1){
      logit = glm(preytype~character,data=datIJ, family="binomial")
      print(logit)
      phylogit = phyloglm(preytype~character,phy=treeIJ,data=datIJ,boot=10, btol=30)
      print(phylogit)
      rowIJ = c(names(logit_diet)[prey], names(dprunedmatrix_logs)[char], phylogit$n, phylogit$aic, coef(summary(phylogit))[2,6], coef(summary(phylogit))[2,1], logit$aic, coef(summary(logit))[2,4], coef(summary(logit))[2,1])
      } else{
      rowIJ = c(names(logit_diet)[prey], names(dprunedmatrix_logs)[char], NA, NA, NA, NA, NA, NA, NA)
      }
    print(rowIJ)
    logits = rbind(logits, rowIJ)
  }
}
logits = logits[-1,]
logits[,4:9] = sapply(logits[,4:9], as.numeric)
logits[,4:9] = sapply(logits[,4:9], function(x){round(x,3)})
write.csv(logits, "diet_morph_logits.csv", row.names = F)
